A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-10-24 rr-flow.Rmd
added disclosures according to AMPPS submission guidelines
added author contributions and conflict of interests

@@

>>>>

# Disclosures

This paper is fully reproducible using the workflow described in this paper. All materials, including the manuscript source and all R codes and files used to generate this manuscript, can be found on the accompanying GitHub repository <https://github.com/aaronpeikert/reproducible-research/>.

@@

## Author Contributions

Aaron Peikert and Andres Brandmaier jointly generated the idea for the manuscript. Aaron Peikert implemented the workflow. Aaron Peikert and Andreas Brandmaier jointly generated the R code examples. Aaron Peikert wrote the first draft of the manuscript, and both authors critically edited it. Both authors approved the final submitted version of the manuscript.

## Conflicts of Interest

The authors declare that there were no conflicts of interest with respect to the authorship or the publication of this article.
